\chapter{Theory}\label{chap:theory}

The Standard Model (SM) of particle physics describes interactions between all known elementary particles via the strong, weak, and electromagnetic forces. It is capable of making astonishingly precise and accurate predictions. For example, the prediction and measurement of the anomalous magnetic dipole moment of the electron agree to one part in $10^{12}$~\cite{Fan:2022eto}. Furthermore, measurements made of high energy collisions, like those at the LHC, remain consistent with SM predictions. However, the SM cannot explain several key observations, including dark matter~\cite{Clowe:2006eq}, neutrino oscillations~\cite{Super-Kamiokande:1998kpq}, and the matter-antimatter asymmetry of the universe~\cite{Canetti:2012zc}. It is anomalies like these that motivate the formulation of theories that go beyond the SM.

Anomalous observations are not the only source of motivation when developing new theories. There are also theoretical problems with the SM such as the hierarchy problem~\cite{Thomson:2013zua} and that the SM does not include a description of gravity. From a scientific perspective, a BSM theory does not need to solve these problems, it only needs to provide predictions that accurately describe our measurements. However, history teaches us that when pursuing solutions to theoretical problems, we can also make scientific breakthroughs. The prediction of the charm quark in 1970~\cite{Glashow:1970gm} before its discovery in 1975~\cite{Cazzoli:1975et} is a great example of this.

This chapter begins with an explanation of the SM, starting with the particle content and the allowed interactions before moving onto a mathematical description of the theory. Following this, the content is tailored towards the results discussed later in this thesis, those being the di-Higgs search in \cref{chap:dihiggs} and the Effective Field Theory (EFT) interpretation in \cref{chap:eft}. This content includes Higgs boson phenomenology at the LHC and relevant extensions to the SM, including EFTs and two BSM theories that motivate the search in \cref{chap:dihiggs}, namely Warped Extra Dimensions (WED) and the Next-to-Minimal Supersymmetric Standard Model (NMSSM).

\input{Chapters/theory/SM.tex}
\input{Chapters/theory/Higgs.tex}
\input{Chapters/theory/BSM.tex}